Appendix to "Integrated nested Laplace approximations for extended latent Gaussian models with application to the Naomi HIV model

### 2023-01-03 src/docs_paper/appendix.Rmd
Jeff's suggested edits to appendix

### ANC testing cascade

For women 15-49 the predicted number of ANC clients $\Psi_{x, a}$ is a log-linear model
$$
\log (\Psi_{x, a}) = \log (N_{x, \text{F}, a}) + \psi_{R_x, a} + \beta^\psi + u_x^\psi
$$
where $N_{x, \text{F}, a}$ are the female population sizes, $\psi_{R_x, a}$ are ASFR in Spectrum region $R_x$ at time $t$, $\beta^\psi$ are the log rate ratio for the number of ANC clients relative to the predicted fertility, $u_x^\psi \sim \mathcal{N}(0, \sigma^\psi)$ are district random effects.
HIV prevalence $\rho_{x, a}^\text{ANC}$ and ART coverage $\alpha_{x, a}^\text{ANC}$ among pregnant women modelled with logit-linear models
\begin{align}
\text{logit}(\rho_{x, a}^{\text{ANC}}) &= \text{logit}(\rho_{x, F, a}) + \beta^{\rho^{\text{ANC}}} + u_x^{\rho^{\text{ANC}}} + \eta_{R_x, a}^{\rho^{\text{ANC}}} \\
\text{logit}(\alpha_{x, a}^{\text{ANC}}) &= \text{logit}(\alpha_{x, F, a}) + \beta^{\alpha^{\text{ANC}}} + u_x^{\alpha^{\text{ANC}}} + \eta_{R_x, a}^{\alpha^{\text{ANC}}},
\end{align}

@@

### ANC attendance

@@

### Awareness of HIV status

The proportion of HIV positive adults aware of their HIV status is $v_{x, s, a}$, and the proportion of untreated HIV positive adults aware of their HIV status is $\tilde \nu_{x, s, a}$ such that
$$
v_{x, s, a} = \alpha_{x, s, a} + \frac{\tilde v_{R_x, s, a}}{1 - \alpha_{x, s, a}}.
$$

>>>>

### ANC testing

HIV prevalence $\rho_{x, a}^\text{ANC}$ and ART coverage $\alpha_{x, a}^\text{ANC}$ among pregnant women modelled with logit-linear models
\begin{align}
\text{logit}(\rho_{x, a}^{\text{ANC}}) &= \text{logit}(\rho_{x, F, a}) + \beta^{\rho^{\text{ANC}}} + u_x^{\rho^{\text{ANC}}} + \eta_{R_x, a}^{\rho^{\text{ANC}}} \\
\text{logit}(\alpha_{x, a}^{\text{ANC}}) &= \text{logit}(\alpha_{x, F, a}) + \beta^{\alpha^{\text{ANC}}} + u_x^{\alpha^{\text{ANC}}} + \eta_{R_x, a}^{\alpha^{\text{ANC}}},
\end{align}

@@

### ART attendance

@@
